%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Most Relevant Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Front End Engineer} % Job title
  {Neoxi} % Organization
  {Istanbul, Turkey (Hybrid)} % Location
  {\acvDateRange{6}{2024}{0}{0}} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Stabilized releases with comprehensive end-to-end and visual tests (\textbf{Jest, Cypress, Playwright}) and pipeline optimizations, reducing continuous integration minutes by approximately 30\% and decreasing production bugs by approximately 30\%, while improving mean time to recovery (MTTR) and release safety.}
      \item {Led a Storybook-driven component library and \textbf{optimized internal tooling}, cutting UI regressions by 35\% and \textbf{improving overall Developer Experience (DX)} across flagship data-heavy, rendering-intensive UIs; authored technical design documentation (ADRs, component specs) to standardize platform usage across teams.}
      \item {Shortened build times by 32\% (from 12.5 to 8.5 mins) and increased deployment frequency by 80\% through the optimization of CI/CD pipelines in \textbf{GitHub Actions}, implementing build caching and automated releases.}
      \item {Decreased API-related bugs by 28\% and reduced redundant data-fetching code by over 20\% by engineering a type-safe layer for both \textbf{RESTful} and \textbf{GraphQL} APIs using Code Generator and reusable \textbf{React Query hooks}.}
      \item {Partnered with backend engineers and product owners to deliver \textbf{LLM-driven} features, ensuring high standards for performance and security through type-safe API layers.}
    \end{cvitems}
  }
  \acvDashedSeparator

  %---------------------------------------------------------
  \cventry
  {Front-End Engineer} % Job title
  {Shop‑Ware} % Organization
  {California, United States (Remote)} % Location
  {\acvDateRange{6}{2022}{5}{2024}} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Guided technical strategy} and authored the migration RFC for a phased Backbone-to-React transition, taking long-term ownership of the frontend platform domain; resulted in 20\% faster initial load and quicker user interaction, utilizing Webpack and feature flags to ensure a seamless transition without service interruption.}
      \item {Mentored 3 mid-level developers through code reviews and technical pairing, establishing frontend standards that improved code quality and reduced UI regressions by 25\%.}
      \item {Decreased page load time by 40\% for shop managers by decomposing a critical page and implementing route-level lazy loading.}
      \item {Accelerated UI delivery speed by 25\% and significantly improved design consistency by building and driving the adoption of a \textbf{Storybook} driven component library with design tokens.}
    \end{cvitems}
  }
  \acvDashedSeparator

  %---------------------------------------------------------
  \cventry
  {Front-End Engineer} % Job title
  {Coffee} % Organization
  {Perth, Australia (Remote)} % Location
  {\acvDateRange{9}{2021}{5}{2022}} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and delivered real-time collaborative meeting tools (\textbf{React/Next.js} + \textbf{WebRTC/Mediasoup}), implementing client-side transport and sync protocols for low-latency multi-user sessions → +15\% team productivity.}
      \item {Integrated \textbf{Jest/Cypress} and \textbf{Sentry} → −30\% production bugs and −10\% \textbf{MTTR}.}
      \item {Collaborated with design to rebuild navigation UI using \textbf{Tailwind CSS}, delivering responsive, cross-browser-compatible interfaces → −20\% client workflow delays.}
      \item {Enforced \textbf{WCAG} accessibility standards across the Storybook component library, ensuring 100\% compliance for enterprise-level client workflows.}
    \end{cvitems}
  }
  \acvDashedSeparator

  %---------------------------------------------------------
  \cventry
  {Front End Developer} % Job title
  {Satek} % Organization
  {Hamedan, Iran (On-site)} % Location
  {\acvDateRange{6}{2019}{9}{2021}} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Upgraded React 15 to 16 and implemented \textbf{Webpack} builds → -30\% bundle size, faster startup and broader device compatibility.}
      \item {Shipped 4 \textbf{Electron} desktop apps (macOS/Windows) with automated packaging → -25\% release cycle, rolled out to 5+ enterprise clients.}
      \item {Enhanced modular, reusable components → +30\% dev speed and -25\% maintenance.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
