%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {SENIOR FRONT END ENGINEER} % Job title
  {Shop-Ware} % Organization
  {San Francisco, California, US} % Location
  {Jun. 2022 - May. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Modernized front-end by migrating from Backbone to React, using webpack and feature flags, cutting initial load time by 20\%.}
      \item {Revamped test suite by fixing flaky tests and restructuring E2E, integration, and unit tests, cutting CI/CD execution time by 25\%.}
      \item {Enhanced the repair order page with code splitting and lazy loading, reducing load time by 40\% for shop managers.}
      \item {Accelerated UI development by 25\% by creating a reusable component library in Storybook, standardizing design patterns, and reducing redundant coding.}
      \item {Performed usability tests with shop users, shared feedback, increased dashboard satisfaction by 25\%.}
      \item {Deployed a centralized monitoring environment (Grafana, InfluxDB, CollectD) which gathers system metrics as well as docker runtime metrics.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
  {Danggeun Pay Inc. (KarrotPay)} % Organization
  {Seoul, S.Korea} % Location
  {Mar. 2021 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Everything that matters.}
      \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
      \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
      \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
      \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
      \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
      \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Front End Engineer} % Job title
  {Coffee} % Organization
  {Perth, Western Australia, Australia} % Location
  {Sep. 2021 - May. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed B2B SaaS features using React, Next.js, and WebRTC, including real-time online meeting tools, boosting productivity by 15\%.}
      \item {Refined front-end architecture by modularizing components and optimizing data handling with React-Query, speeding up page loads by 50\% and cutting development time by 25\%.}
      \item {Reduced bugs by 30\% with Jest unit/integration tests, Cypress E2E testing, and Sentry error tracking, cutting resolution time by 10\%.}
      \item {Spearheaded communication across cross-functional teams, streamlining navigation and cutting client workflow delays by 20\%.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Front End Engineer} % Job title
  {Satek} % Organization
  {Hamedan, Iran} % Location
  {Jun. 2019 - Sep. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered B2B desktop applications using React, Redux, and Electron.js, streamlining client workflows for 5+ enterprise customers.}
      \item {Redesigned application architecture with modular components and reusable patterns, speeding development by 30\% and cutting maintenance time by 25\%.}
      \item {Mentored three junior developers through training, code reviews, and structured learning, boosting their delivery speed by 40\%.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
