%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Team Lead} % Job title
    {\href{https://dojeldi.org/}{Dojeldi}} % Organization
    {Tehran, Iran} % Location
    {Jun. 2021 - Jan. 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Directed engineering team using Next.js, React, and TypeScript to develop an e-commerce platform, achieving 30\% faster load times and improving retention among 100K+ users.}
            \item {Implemented targeted SEO strategies using Google Analytics and keyword optimization, boosting organic traffic by 40\%
                        and improving search visibility for book-related queries.}
            \item {Optimized platform performance by refactoring front-end code and implementing lazy loading, increasing page speed and reducing bounce rate by 20\%.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Team Lead} % Job title
    {\href{https://irapardaz.ir/}{Ira Pradaz}} % Organization
    {Tehran, Iran} % Location
    {Mar. 2021 - Jun. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Managed the front-end development team for a Vue.js application for a data processing company's website, which serves over 70k+ users.}
            \item {Created a responsive user interface using Tailwind CSS, resulting in a 25\% increase in user engagement.}
            \item {Enhanced website accessibility and optimized performance, achieving a 30\% reduction in page load times.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
